GMU MS SWE Handbook\\{\large A Handbook For the Masters of Software Engineering program at George Mason University

### 2024-03-20 ms-swe-handbook.tex
Updates from Overleaf

\title{Demystifying the Computer Science \\
  PhD Admission in the US\\{\large A Guideline for International \emph{and Domestic} Students}}

@@

\begin{itemize}
\item COMP 501 Computer Programming Foundations I or SWE 510 Object Oriented Programming in Java
\item COMP 502 Mathematical Foundations of Computing I or INFS 501 Discrete and Logical Structures for Information Systems
\item COMP 503 Computer Systems Foundations I or INFS 515 Computer Organization
\item COMP 511 Computer Programming Foundations II or INFS 519 Program Design and Data Structures
\end{itemize}

@@

Students are required to complete 30 credits corresponding to 10 graduate courses. Students are encouraged to download the course planner spreadsheet, and update it as they proceed through the program.

The course work is divided into three categories: 12 credits of core courses, software engineering related courses of 9 credits, and 9 credits of elective courses.

@@

\begin{enumerate}
    \item SWE 619 Object-Oriented Software Specification and Construction
    \item SWE 621 Software Modeling and Architectural Design
    \item SWE 632 User Interface Design and Development
    \item SWE 637 Software Testing
\end{enumerate}

@@

\begin{itemize} 
\item Software Engineering (SWE)
\begin{itemize}
    \item Any SWE courses at the \href{https://catalog.gmu.edu/courses/swe/}{600 level or above}
\end{itemize}
\item Computer Science (CS)

\begin{itemize}
    \item CS 540 Language Processors
    \item CS 550 Database Systems
    \item CS 555 Computer Communications and Networking
    \item CS 571 Operating Systems
    \item CS 584 Theory and Applications of Data Mining
    \item CS 675 Distributed Systems
    \item CS 678 Advanced Natural Language Processing
\end{itemize}

@@

\chapter{Obtaining Funding}
\section{NSF and other Government Funding}

\paragraph{Other Government Funding}

\section{Internal Funding}

\section{Industrial Gifts}

\chapter{Teaching}
\section{Teaching Load}
\section{Teaching Evaluation}
\section{Teaching Philosophy}
\section{Teaching Awards}

\chapter{Mentoring}
\section{Mentoring Undergraduate Students}
\section{Mentoring Graduate Students}
\section{Mentoring Postdocs}
\section{Mentoring Junior Faculty}

\chapter{Services}

\section{Service to your Professional Community}
\section{Service to the Department}
\section{Service to the University}
\section{Service to the Community}

>>>>

\title{GMU MS SWE Handbook\\{\large A Handbook For the Masters of Software Engineering program at George Mason University}}

@@

\begin{itemize}
\item \textbf{COMP 501} Computer Programming Foundations I or \textbf{SWE 510} Object Oriented Programming in Java
\item \textbf{COMP 502} Mathematical Foundations of Computing I or \textbf{INFS 501} Discrete and Logical Structures for Information Systems
\item \textbf{COMP 503} Computer Systems Foundations I or \textbf{INFS 515} Computer Organization
\item \textbf{COMP 511} Computer Programming Foundations II or \textbf{INFS 519} Program Design and Data Structures
\end{itemize}

@@

Students are required to complete \textbf{30 credits} corresponding to \textbf{10 graduate courses}. Students are encouraged to download the course planner spreadsheet, and update it as they proceed through the program.

The course work is divided into three categories: 12 credits of core courses, 9 credits of SWE related courses, and 9 credits of elective courses.

@@

\begin{enumerate}
    \item \textbf{SWE 619} Object-Oriented Software Specification and Construction
    \item \textbf{SWE 621} Software Modeling and Architectural Design
    \item \textbf{SWE 632} User Interface Design and Development
    \item \textbf{SWE 637} Software Testing
\end{enumerate}

@@

\begin{itemize} 
\item Software Engineering
\begin{itemize}
    \item Any SWE courses at the \href{https://catalog.gmu.edu/courses/swe/}{600 level or above}
\end{itemize}
\item Computer Science

\begin{itemize}
    \item CS 540 Language Processors (Compilers)
    \item CS 550 Database Systems
    \item CS 555 Computer Communications and Networking
    \item CS 571 Operating Systems
    \item CS 584 Theory and Applications of Data Mining
    \item CS 675 Distributed Systems
    \item CS 678 Advanced Natural Language Processing
\end{itemize}

@@
